\Large \bf Byteboy : A Byteman Companion application

### 2017-12-07 final-paper/paper.la_.tex
feat(paper): added observations section

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Byteboy : A Byteman Companion Application}

@@

In this paper, we propose Byteboy, a companion application for Byteman. Byteboy provides functionality for manual and semi-automatic rule generation, fuzz test generation, and a Visual Studio Code Byteman rule language extension. Byteboy was designed to improve the Byteman user experience from the point of rule inception, through to actually implementing and shipping the proposed bug-fixing rule file.

@@

Discuss the outputted rules from Byteboy.

@@

>>>>

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Byteboy : A Byteman Companion application}

@@

In this paper, we propose Byteboy\cite{byteboy}, a companion application for Byteman. Byteboy provides functionality for manual and semi-automatic rule generation, fuzz test generation, and a Visual Studio Code Byteman rule language extension. Byteboy was designed to improve the Byteman user experience from the point of rule inception, through to actually implementing and shipping the proposed bug-fixing rule file.

@@

Each of the four programs were able to have at least some sort of their execution behaviour traced by using the set of rules which were automatically generated by Byteboy. The majority of the four program's don't exhibit complex function interactions, so the traceln results aren't as verbose as they could be in an application of larger scale. However, for an average developer looking to see where their program may be getting into trouble, these generated rules should be of some use.

The fuzz test rules varied in their range of effectiveness, and their results will be explained individually.

    {\tt A.java}: In the case of this program, the variable supplied to the {\tt A()} function is passed into a constructor for {\tt JFrame()}, and as a result, substituting the value of this variable has little to no effect on the application's behaviour. In this case, the fuzz test rule works only in the sense that it can be run and changes the title of the produced JFrame, but has no effect on the rest of the program's execution.

{\tt InfLoop.java}: In this program, an infinite loop is entered because the {\tt doWork()} function gets passed a variable with the value of 0, which causes a while loop to start. This while loop has no exit condition, and as a result, the program loops forever. Fortunately, the fuzz test re-assigns the value of the variable which the loop in {\tt doWork()} evaluates in order to start looping. In the case that the fuzz test generates the value of 0, then the program will infinitely loop as previous. However, it is highly likely that a non-zero value will be produced from the fuzz test randomizer, which will allow the program to bypass the infinite loop completly, thus ceasing execution of the program.

{\tt Question3.java}: This program accepts 10 integers as input, and attempts to calculate the average. The fuzz test generator targets the function responsible for calculating the average, but unfortunately the program throws an {\tt ArrayOutOfBoundsException} and crashes before the fuzzed value can be substituted. Unfortunately, the generated fuzz test rules will not have a chance to operate in this example, because of the nature of the error.

@@

\bibitem{byteboy}
Byteboy.
\\\texttt{https://github.com/aptmac/byteboy}
